%-------------------------------------------------------------------------------
% This file contains the title, author and abstract.
% It also contains all relevant document numbers used for an ATLAS note.
%-------------------------------------------------------------------------------

% Title
\AtlasTitle{Search for new phenomena in dijet events using quark/gluon
tagging based on track multiplicty} 

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{0.1}

% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
A search for new resonance decays producing a pair of jets is
performed using 139~fb$^{-1}$ of ATLAS $pp$ collision data recorded from the
Large Hadron Collider operating at $\sqrt{s} = 13$~TeV. 
To increase the sensitivity to observe new resonances preferentially
decaying to one or more gluons, a gluon-tag method based on the number
of associated particle tracks is employed.
No significant excess of events above a smoothly falling dijet
background distribution is observed.
The results are used to set cross-section upper limits at the 95\%
confidence level for signal-gluon and double-gluon tagged jets
originating from new resonance decays.
Model-dependent string scale lower limits are set on string resonances
which predominantly decay to a gluon and quark, and mass lower limits
on a massive colour-singlet scalar particle decaying exclusively to
two gluons.  
}

% Author - this does not work with revtex (add it after \begin{document})
%\author{The ATLAS Collaboration}

% Authors and list of contributors to the analysis
% \AtlasAuthorContributor also adds the name to the author list
% Include package latex/atlascontribute to use this
% Use authblk package if there are multiple authors, which is included by latex/atlascontribute
% \usepackage{authblk}
% Use the following 3 lines to have all institutes on one line
%%%%\makeatletter
%%%%\renewcommand\AB@affilsepx{, \protect\Affilfont}
%%%%\makeatother
% \renewcommand\Authands{, } % avoid ``. and'' for last author
% \renewcommand\Affilfont{\itshape\small} % affiliation formatting
% Alphabetising

\AtlasAuthorContributor{Iain Bertram}{a}{Contact, supervising Rybacki, q/g tagging optimisation of selection, statistical framework.}
\AtlasAuthorContributor{Jyoti Prakash Biswal}{b}{BG estimation, systematics.}
\AtlasAuthorContributor{Doug Gingrich}{b,c}{Supervising Lyons.}
\AtlasAuthorContributor{Shih-Chieh Hsu}{d}{Supervising students, checking analysis flow, data MC comparison.}
\AtlasAuthorContributor{Shu Li}{e}{ Supervising students}
\AtlasAuthorContributor{Jack Lindon}{b}{ Data Fitting, Statistical Studies.}
\AtlasAuthorContributor{Fairhurst Lyons}{b}{BG estimation, systematics.}
\AtlasAuthorContributor{Ben Nachman}{f}{CP uncertainties; supervising Rybacki.}
\AtlasAuthorContributor{Nishu Nishu}{b}{Analysis advice.}
\AtlasAuthorContributor{Katherine Rybacki}{a}{q/g tagging systematics, sample production.}
\AtlasAuthorContributor{Wanyun Su}{e}{Checking analysis flow, data MC comparison.}
\AtlasAuthorContributor{Changxu Wei}{g}{Checking analysis flow, data MC comparison.}
\AtlasAuthorContributor{Dengfeng Zhang}{b}{Ntuple Creation, Optimisation of Data Selection}
\AtlasAuthorContributor{Yan Zhou}{g}{Checking analysis flow, data MC comparison.}
% \AtlasContributor{.}
% \author[a]{Iain Bertram}
% \author[a]{Second Author}
% \author[b]{Third Author}
\affil[a]{Lancaster University, United Kingdom}
\affil[b]{University of Alberta, Canada}
\affil[c]{TRIUMF, Canada}
\affil[d]{University of Washington, United States of America}
\affil[e]{Tsung-Dao Lee Institute, China}
\affil[f]{Lawrence Berkeley National Laboratory, United States of America}
\affil[g]{Tsinghua University, China}

% If a special author list should be indicated via a link use the following code:
% Include the two lines below if you do not use atlasstyle:
% \usepackage[marginal,hang]{footmisc}
% \setlength{\footnotemargin}{0.5em}
% Use the following lines in all cases:
% \usepackage{authblk}
% \author{The ATLAS Collaboration%
% \thanks{The full author list can be found at:\newline
%   \url{https://atlas.web.cern.ch/Atlas/PUBNOTES/ATL-PHYS-PUB-2016-007/authorlist.pdf}}
% }

% ATLAS reference code, to help ATLAS members to locate the paper
\AtlasRefCode{ANA-EXOT-2019-32}

% ATLAS note number. Can be an COM, INT, PUB or CONF note
\AtlasNote{ANA-EXOT-2019-32-INT1}
